Algorithm explanation

### 2013-08-25 article/algo.tex
Small fixes

The construction of the algorithm roughly consists of two parts.
\begin{itemize}
\item \textbf{Iterative Constraint Generation} is a process to build a
  constraint to compute a solution.  It starts from generating the
  weakest constraint in the sense that the resulting solution would
  not be simple yet.  The process iteratively strengthen a constraint
  until the strongest one while preserving the constraint
  satisfiability.  The strongest constraint gives a simple solution.
\item \textbf{Problem Restructuring} If the constraint become
  unsatisfiable during the iteration, the process restructure the
  problem equivalent to obtain a less simpler solution.  This process
  considers the unsatisfiable core of the constraint.
\end{itemize}

@@

The novelty of our algorithm lies in the incremental constraint
refinement.  The algorithm try from the weakest constraint that an
input problem allows that does not give a simple solution, and
strengthen the constraint until it reaches to the simplest solution
that the problem has.  When a constraint becomes unsatisfiable, the
algorithm analyzes the unsatisfiable core and transform the problem to
obtain less simple solution.

This construction of the algorithm enables us to compute a relatively
simpler solution compared to existing algorithms in a reasonable time.

>>>>

The construction of the algorithm roughly consists of two parts.
\begin{itemize}
\item \textbf{Iterative Constraint Generation} is a process to build a
  constraint to compute a solution.  It starts from generating the
  weakest constraint in the sense that the resulting solution would
  not be simple yet.  The process iteratively strengthen a constraint
  until the strongest one while preserving the constraint
  satisfiability.  The strongest constraint gives a simple solution.
\item \textbf{Problem Restructuring} is a process to restructure the
  problem to obtain a less simpler solution, if the constraint become
  unsatisfiable during the iterative constraint generation.  This
  process considers the unsatisfiable core of the constraint, and
  wisely enlarge the solution size.
\end{itemize}

@@

The novelty of our algorithm lies in the incremental constraint
refinement.  The algorithm tries to solve from the weakest constraint
that an input problem allows that does not give a simple solution, and
gradually strengthen the constraint until it reaches to the simplest
solution that the problem has.  When a constraint becomes
unsatisfiable during this step, the algorithm analyzes the
unsatisfiable core and transform the problem to obtain a less simple
solution.

This construction of the algorithm enables us to compute a relatively
simpler solution compared to existing algorithms while preserving the
computation cost in a reasonable time.
